Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-12 response.md

-----------------------------------
Minor Comment 4
-----------------------------------

***4) I probably should have mentioned this above, but why are the authors not working with equation (4) as the basis of their regression model?***

Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1. However, the original version of Equation 4 could produce vote fractions greater than 1 for certain combinations of z and f_0 if left in the same form as Equation 2. We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader. Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3). All data in the tables and catalog have been updated to account for these small changes.

The attached figure displays the effect of this change. Shown is the distribution of the change in debiased f_features between this draft (new normalization) and the previous draft (old normalization). For the correctable sample of galaxies, the new debiased f_features vote fractions are on average 0.02 greater than the previous draft, and at maximum 0.06 greater. These changes are too small to significantly affect any final morphologies.

ATTACH: https://github.com/willettk/gzhubble/blob/master/python/notebooks/compare_new_debiased_fraction_hist.png

### 2016-09-15 response.md

***I believe that Section 4.2 should come first: present the FERENGI sample,
and discuss the scheme used to select those data that are to be analyzed to
determine the debiasing correction. Then the details of the statistical model
for debiasing (currently in Section 4.1) should come next.***

***Section 4.3 is fine where it is placed. (However, see minor comment 10
below, which actually is not quite as minor as the other comments.)***

Section 4 has been re-organized in the manner suggested by the reviewer. The
authors agree this structure will be more clear to the readers.

========== Major Issue II: Statistical Model
------------------------------------------

@@

***Due to the length of Major Issue II, it is placed at the end of this
response.***

We used the referee's input to review and revise the fitting of the
artificially-redshifted images (from FERENGI) and construction of the debiasing
equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_0, including linear, quadratic,
cubic, and exponential dependences on redshift; for each of these functional
forms, we also tested combinations using either a constant zeta parameter or a
zeta function that linearly depends on surface brightness. We compared the
relative quality of fits using the Akaike information criteria (AIC); for each
case, we found no significant differences in the results based on the choice of
model. Full details and code for these tests can be viewed in this Python
notebook:

https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb

@@

***4) I probably should have mentioned this above, but why are the authors not
working with equation (4) as the basis of their regression model?***

Equation 2 was originally left unbounded because the raw data being fit was
inherently bounded between vote fractions of 0 and 1. However, the original
version of Equation 4 could produce vote fractions greater than 1 for certain
combinations of z and f_0 if left in the same form as Equation 2. We have
realized that the difference in normalization, while having only a small effect
on the fitting of the data, is inconsistent and may be confusing to a reader.
Therefore, we have changed Equation 2 to match Equation 4 (see response to
Major Comment II, as well as Minor Comment 3). All data in the tables and
catalog have been updated to account for these small changes.

The attached figure displays the effect of this change. Shown is the
distribution of the change in debiased f_features between this draft (new
normalization) and the previous draft (old normalization). For the correctable
sample of galaxies, the new debiased f_features vote fractions are on average
0.02 greater than the previous draft, and at maximum 0.06 greater. These
changes are too small to significantly affect any final morphologies.

ATTACH:
https://github.com/willettk/gzhubble/blob/master/python/notebooks/compare_new_debiased_fraction.png

@@

---------------------------------- Minor Comment 7
----------------------------------

***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until
the contamination from both groups is minimized." If I look at Figure 9, it
would appear that the correctable and lower-limit regions can be perfectly
separated (using a tree, for instance). Am I wrong about this?***

The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in
f_features-redshift space, but there are a few regions near the edges in which
there is overlap between the two populations. This is affected slightly in the
figure by the choice of bin size and location. However, our analysis makes the
assumption that a true/physical separation should be a smooth function of
z-mu-f. Implementing a convex hull in this space created a very small volume
near the edge of the inner convex hull that had overlapping positive and
negative data points; we optimize the overall accuracy of the hull by adjusting
the outer boundaries as described in what is now Section 4.1.

Use of a different method such as a tree could potentially prove to be a
superior separator. However, the new normalization technique used in this draft
results in very clean separation based on the convex hull, with only a single
adjustment; see:

https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb

Further optimization would have an extremely minimal effect on the overall
results.

@@

---------------------------------- Minor Comment 11
----------------------------------

***11) Section 7.3: "external pulblications" -> "external publications"***

Thank you, this typo has been fixed in the text.

------------------------------- ***Major Issue II***
----------------------------------

### 2016-09-30 writeup/gz_hubble_data.tex
adding referee acknowledgement
addressing minor comments 3 and 4 on figure 9

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
analysis was initiated. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
in producing Figure~\ref{fig:decisiontree}.

>>>>

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with evolutionary correction $e=0$ and at least three detectable images 
in redshift bins of $z\ge0.3$. The displayed bins are sorted by \ffeaturesrest, 
labeled above each plot. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
analysis was initiated. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
in producing Figure~\ref{fig:decisiontree}. We thank Nathan Cloutier and Brent
Hilgart for useful discussions. We also thank the referee for thoughtful comments
which improved the quality of this paper.
